A sample workflow

### 2025-05-01 analyses/lpiworkflow.qmd
small additions

To show our workflow in action, we examine a subset of the Living Planet Index (LPI, download at: https://www.livingplanetindex.org/data_portal. This download should include a csv file, here: LPD2022_public.csv, that we use below). We discuss the LPI in the main text; for more information, check out: www.livingplanetindex.org/.

**Note**: data from Jonathan comes from *LivingPlanetIndexDatabase_2025-02-01_19.19.51*.

@@

@@

```{r}
wd <- "/home/victor/projects/forecastflows/analyses"

@@

@@

For now, we also take a look at how model fits look against the simulated data:

>>>>

To show our workflow in action, we examine a subset of the Living Planet Index (LPI, download at: https://www.livingplanetindex.org/data_portal. This download should include a csv file, here: LPD_2024_public.csv, that we use below). We discuss the LPI in the main text; for more information, check out: www.livingplanetindex.org/.

@@

::: {.callout-tip appearance="simple" icon=false}

@@

:::

wd <- "/home/victor/projects/forecastflows/analyses"

@@

:::

@@

For now, we also take a look at how model fits look against the simulated data (error bars and ribbon represent the 95% credible intervals):
